### 2020-11-10 thesis/chap_2.tex
comment 54

In order to understand what stakeholders perceive as a conservation priority, and derive conservation scenarios from those perceptions, we conducted a community workshop. The workshop was approved by McGill University’s Research Ethics Board (see Appendix 2 for the approval letter). The workshop was held on January 22nd 2020 in the public library of Saint-Jean sur Richelieu. \\

>>>>

In order to understand what stakeholders perceive as a conservation priority, and derive conservation scenarios from those perceptions, we conducted a community workshop (a conceptual figure of the methodology is to be found in Appendix 2 under the form of the Workshop participant roadmap). The workshop was approved by McGill University’s Research Ethics Board (see Appendix 2 for the approval letter). The workshop was held on January 22nd 2020 in the public library of Saint-Jean sur Richelieu. \\
